\bf Drift Removal for Time Series Data Using Quantile Trend Filtering

### 2018-12-07 Manuscript/simulation_notes.tex
updated eBIC function to have scale parameter

	\item \texttt{detrendr\_SIC}: Our method where we minimize
	$\sum_i\rho_{\tau}(y_i - \theta_i) + \lambda||D\theta||_1$ and $\lambda$ is chosen using SIC from above. A single value of $\lambda$ was chosen by scaling and summing SIC values across all quantiles. 
	\item \texttt{detrendr\_valid}: Our method where lambda is chosen by leaving out every 5th observation as a validation data set and evaluating the check loss function on the validation data. 
\end{itemize}

>>>>

	\item \texttt{detrendr\_SIC}: Our method where we minimize
	$\sum_i\rho_{\tau}(y_i - \theta_i) + \lambda||D\theta||_1$ and $\lambda$ is chosen using SIC from above. A single value of $\lambda$ was chosen by scaling and summing SIC values across all quantiles. 
	\item \texttt{detrendr\_valid}: Our method where lambda is chosen by leaving out every 5th observation as a validation data set and evaluating the check loss function on the validation data.
	\item \texttt{detrendr\_eBIC}:   The traditional BIC is given by 
	\begin{equation}
	\mbox{BIC}(s) = -2\log(L\{\hat{\theta}(s)\}) + \nu(s)\log n 
	\end{equation}	
	where $\theta(s)$ is the parameter $\theta$ with those components outside $s$ being set to 0, and $\nu(s)$ is the number of components in $s$. If we assume an asymmetric Laplace likelihood $L(y|\theta) = \left(\frac{\tau^n(1-\tau)}{\sigma}\right)^n\exp\left\{-\sum_i\rho_\tau(\frac{y_i - \theta_i}{\sigma})\right\}$ and the number of non-zero elements of $D\theta$ as $df$
	\begin{equation}
	\mbox{BIC}(df) = 2\sum_i\frac{1}{\sigma}\rho_{\tau}(y_i-\theta_i) + df\log n
	\end{equation} 
	We can choose and $\sigma>0$ and have found empirically that $\sigma =  \frac{1-|1-2\tau|}{2}$ produces stable estimates. \cite{chen2008} proposed the extended BIC for large parameter spaces 
	\begin{equation}
	BIC_{\gamma}(s) = -2\log(L\{\hat{\theta}(s)\}) + \nu(s)\log n  + 2\gamma\log{P\choose j}
	\end{equation}
	where $P$ is the total number of possible parameters and $j$ is the number of parameters included in given model.

\end{itemize}
